### 2020-02-12 README.rmd

<!-- Code status -->
[![Build Status](https://travis-ci.org/MKLau/Rclean.svg?branch=master)](https://travis-ci.org/MKLau/Rclean) 
[![Coverage status](https://codecov.io/gh/MKLau/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/MKLau/Rclean?branch=master)

@@

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
    scientists more *easily* write “cleaner” code.
- Written with research scientists that are results oriented in mind,
    the package’s primary function provides a simple way to isolate
    the minimal code you need to produce a specific result, such as a
    statistical table or a figure. By focusing on specific results
    (aka. variables), large and/or complicated analytical scripts can
    be paired down to the essentials and easily re-factored to be more
    robust and easily shared.
- Below, you'll find a brief introduction to get you started using the
  package. For more details, see `vignette("Rclean")`.

>>>>

<!-- Code status -->
[![Build Status](https://travis-ci.org/ROpenSci/Rclean.svg?branch=master)](https://travis-ci.org/ROpenSci/Rclean) 
[![Coverage status](https://codecov.io/gh/ROpenSci/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/ROpenSci/Rclean?branch=master)

@@

- [Rclean](https://github.com/MKLau/Rclean) was created to help
    scientists more *easily* write “cleaner” code.
- Written with research scientists that are results oriented in mind,
    the package’s primary function provides a simple way to isolate
    the minimal code you need to produce a specific result, such as a
    statistical table or a figure. By focusing on specific results
    (aka. variables), large and/or complicated analytical scripts can
    be paired down to the essentials and easily re-factored to be more
    robust and easily shared.
- Below, you'll find a brief introduction to get you started using the
  package. For more details, see `vignette("Rclean")`.
